### 2015-11-14 thesis-proposal/problem.tex
Updated timeline

\item The final premise valides the expansion by checking the marked expansion against the type specified by the TSM, and generates the final expansion, $e$, according to the rules defining the \emph{expansion validation judgements}:

@@

In the dissertation, I plan to first describe the simplest style of TSMs (i.e. unparameterized expression TSMs) by example. This is \textbf{complete}. I will next present a formal system that formalizes such TSMs. The account in Sec. \ref{sec:tsm-formalism} represents the first and most substantial step of this plan. This is complete on paper, so I mainly need to typeset the omitted details, including the metatheory. I have made substantial progress as of this writing (see link below) and I plan to finish this by the \textbf{middle of November}. This system will serve as the basis for several extensions that capture other constructs described above, so I will ask the committee to read this section in detail once it is complete.

The first extension will add support for pattern matching. I will base this extension on the account of pattern matching given in \emph{PFPL} \cite{pfpl}. I plan to have a rough sketch of how this should work by \textbf{late-November}, in consultation with the committee, and a final write-up by Black Friday (i.e. the \textbf{third week of December}).

The next extension will add support for value, type and module parameters. To do so, I will assume that the available module paths and their signatures are being tracked by a module context in the static semantics, without detailing how the module language populates this context (i.e. I will only specify the ``core language''). I plan to sketch this out and discuss it with my committee \textbf{during November and December} and finish writing the details up by the \textbf{beginning of Spring semester}.

Beginning in the \textbf{Spring semester}, I will write up the work on type-specific languages. A variant of this work has been published already, and the groundwork for it will have already been laid down in the earlier chapters, so I anticipate being done with this by \textbf{the second week of February}. I will finish the remaining sections (e.g. additional background, related and future work sections, and additional examples), flesh out the proofs of minor lemmas and respond to the committee's requests for edits for the remainder of the semester. Based on this timeline, I plan to defend before the \textbf{end of the Spring 2016 semester}.

>>>>

\item The final premise validates the expansion by checking the marked expansion against the type specified by the TSM, and generates the final expansion, $e$, according to the rules defining the \emph{expansion validation judgements}:

@@

In the dissertation, I plan to first describe the simplest style of TSMs (i.e. unparameterized expression TSMs) by example. This is \textbf{complete}. I will next present a formal system that formalizes such TSMs. The account in Sec. \ref{sec:tsm-formalism} represents the first and most substantial step of this plan. A complete draft of this chapter, with the exception of proofs at the end, is \textbf{complete}. I plan to finish the proofs by \textbf{Nov. 19}. This system will serve as the basis for several extensions that capture other constructs described above, so I will ask the committee to read this section in detail once it is complete.

The first extension will add support for pattern matching. I will base this extension on the account of pattern matching given in \emph{PFPL} \cite{pfpl}. I plan to have a rough sketch on paper of how this should work by \textbf{Dec. 2} and a draft of the chapter (excepting complete proofs) by Black Friday (i.e. the \textbf{third week of December}).

The next extension will add support for type and module parameters. To do so, I will assume that the available module paths and their signatures are being tracked by a module context in the static semantics, without detailing how the module language populates this context (i.e. I will only specify the ``core language''). I plan to sketch this out and discuss it with my committee \textbf{during November and December} and finish writing the details up by the \textbf{beginning of Spring semester}.

Beginning in the \textbf{Spring semester}, I will be working half-time on a new grant and half-time on finishing the dissertation. The first task will be to write up the work on type-specific languages. A variant of this work has been published already, and the groundwork for it will have already been laid down in the earlier chapters, so I anticipate being done with this by \textbf{the end of February}. I will finish the remaining sections (e.g. additional background, related and future work sections, and additional examples), flesh out the proofs of minor lemmas and respond to the committee's requests for edits for the remainder of the semester. Based on this timeline, I plan to have a completed draft of the dissertation by the \textbf{end of beginning of April} and defend before the \textbf{end of the Spring 2016 semester}.
